{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-09-30 paper/tex/sections/variations.tex
remove a todo
ce trends

\todo{Discuss $\alpha_{\rm CE}$ changes: It seems that alpha=1 is a sweet spot for BHBH and BHNS (they seem to follow the same trend) whilst NSNS has a very different pattern -- not really sure what's happening here}

We explore the optimistic CE scenario in model \modOpt{}, meaning that we allow Hertzsprung gap donors to survive CE events. A large fraction of the progenitors of the BHs in our sample expand significantly during the Hertzsprung gap phase and initiate CE events. This means that, when we assume the optimistic CE scenario, the formation rate of BHs is greatly increased. Therefore, we find that, though the detectable \textit{fraction} does not change significantly, the increased formation rate of BHs in the Milky Way leads to this model predicting significantly more BHBH detections.

@@

\subsubsection{Other interesting features}
\todo{maybe add CE model stuff}

>>>>

Models \modAlphaLowest{}-\modAlphaHighest{} alter $\alpha_{\rm CE}$, the common-envelope efficiency parameter, to $0.1, 0.5, 2.0$ and $10.0$ respectively (where the fiducial model has $\alpha_{\rm CE} = 1.0$). Although we see that there are large variations in the LISA detection rates when changing $\alpha_{\rm CE}$, the detectable \textit{fraction} of systems remain largely unchanged. Therefore, any changes in the detection rate are due to changes in the \textit{formation} rate of the DCOs.

\todo{Explain formation rate differences with $\alpha_{\rm CE}$ changes. I'm pretty sure this comes down to higher alpha leading to larger separations but also fewer stellar mergers and this affects NSNSs and BHBH/BHNSs differently since the ejection of the envelope is very mass dependent. I'm making plots to show this (got sidetracked by orientation)}

We explore the optimistic CE scenario in model \modOpt{}, meaning that we allow Hertzsprung gap donors to survive CE events. A large fraction of the progenitors of the BHs in our sample expand significantly during the Hertzsprung gap phase and initiate CE events. This means that, when we assume the optimistic CE scenario, the formation rate of BHs is greatly increased. Therefore, similar to models \modAlphaLowest{}-\modAlphaHighest{}, we find that though the detectable \textit{fraction} does not change significantly, the increased formation rate of BHs in the Milky Way leads to this model predicting significantly more BHBH detections.

@@
